Teton Mountain Runs 50K

### 2024-03-05 msu-masters.qmd
Update website 4/5/24

---
<figure>
  <img src="img/msu-masters/cages.heic" alt="Montana State University" 
  width = 250" height = "200">
</figure>

<figure>
  <img src="img/msu-masters/vcs.heic" alt="Montana State University" 
  width = 200" height = "300">
</figure>

<figure>
  <img src="img/msu-masters/field.heic" alt="Montana State University" 
  width = 250" height = "200">
</figure>

>>>>

---

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Box with Rounded Edges</title>
<style>
  .container {
    width: 400px;
    height: auto; /* Set container height */
    border: 0.5px solid #ccc; /* Light grey color */
    border-radius: 8px; /* Less rounded edges */
    overflow: hidden; /* Hide overflow content */
    position: relative;
    display: inline-block;
    transition: box-shadow 0.15s ease; /* Transition for box-shadow */
    box-shadow: 0 2px 5px rgba(0, 0, 0, 0.1); /* Slight shadow by default */
    text-align: center; /* Center content horizontally */
    text-decoration: none; /* Remove underline */
    margin-right: 20px; /* Add margin to create space between boxes */
  }

  .container:last-child {
    margin-right: 0; /* Remove margin from the last box */
  }

  .container:hover {
    box-shadow: 0 10px 20px rgba(0, 0, 0, 0.1); /* Increased shadow on hover */
  }

  .content {
    width: 100%;
    height: 100%;
    padding: 20px;
    box-sizing: border-box;
  }

  .content img {
    width: 50%;
    height: auto;
    display: block;
    margin: 0 auto; /* Center the image horizontally */
    object-fit: cover; /* Crop the image to cover container */
  }

  .text {
    margin-top: 10px;
    text-align: center; /* Center text within the box */
    text-decoration: none;
  }

  .text h1 {
    font-size: 24px; /* Larger text size */
    margin-top: 1px;
    margin-bottom: 5px; /* Adjust margin between large and small text */
    color: black;
  }
  .text h1:hover {
    color: #2068DC; /* Change text color to blue on hover */
  }

  .text p {
    font-size: 14px;
    margin-top: 5px;
    color: #666;
  }
</style>
</head>
<body>
  <a href="wss.qmd" class="container">
    <div class="content">
      <img src="img/msu-masters/wss.JPG" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1>Wheat Stem Sawfly</h1>
        <p>Understanding the importance of smooth brome in promoting a Braconid parasitoid that targets the Wheat Stem Sawfly.</p>
      </div>
    </div>
  </a>
  <a href="https://www.example.com" class="container">
    <div class="content">
      <img src="img/msu-masters/loco-bee2.jpg" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1>Locoweed Volatiles</h1>
        <p>Comparison of volatile organic compounds profiles of <em>Oxytropis</em> plants that contained the commensal endophyte <em>Alternaria oxytropis</em> and those that did not.</p>
      </div>
    </div>
  </a>
</body>
</html>

```

### 2024-03-05 pfreport.qmd
Update website 4/5/24

---
title: "MT Post Farm Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_collapsed: false
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console

website:
  sidebar:
    style: "docked"
    contents:
      - section: "Test1"
        contents: index.qmd
      - section: "Test2"
        contents: index.qmd
---
```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```
```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")

@@

# POST FARM

>>>>

---
title: "MT Post Farm Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_collapsed: false
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console
---
```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```
```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")

@@

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Image Cropping Example</title>
<style>
    }
    .image-container {
        width: auto; /* Set the width of the container */
        height: auto; /* Set the height of the container */
        overflow: hidden; /* Hide overflow */
    }
    .image-container img {
        width: 100%; /* Make the image fill the container horizontally */
        height: auto; /* Maintain aspect ratio */
        object-fit: cover;
        object-position: center;
    }
</style>
</head>
<body>

<div class="image-container">
    <img src="img/msu-masters/cages-wide.jpg" alt="Your Image">
</div>

</body>
</html>

```
# POST FARM

### 2024-03-05 projects.qmd
Update website 4/5/24

---
title: "Projects"
editor_options: 
  chunk_output_type: console
---
::: {style="display: flex;"}

<figure style="margin-right: 20px; display: flex; flex-direction: column; align-items: center;">
  <a href="msu-masters.qmd">
    <img src="img/msu-logo.jpg" alt="Montana State University" width="200" height="200">
  </a>
  <figcaption style="text-align: center;">Montana State University</figcaption>
</figure>

<figure style="margin-right: 20px; display: flex; flex-direction: column; align-items: center;">
  <a href="bballref.qmd">
    <img src="img/bballref-logo.jpeg" alt="Basketball Reference Tool" width="200" height="200">
  </a>
  <figcaption style="text-align: center;">Basketball Reference Tool</figcaption>
</figure>

:::

>>>>

---
title: "Projects"
editor_options: 
  chunk_output_type: console
---

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Box with Rounded Edges</title>
<style>
  .container {
    width: 300px;
    height: 300px; /* Set container height */
    border: 0.5px solid #ccc; /* Light grey color */
    border-radius: 8px; /* Less rounded edges */
    overflow: hidden; /* Hide overflow content */
    position: relative;
    display: inline-block;
    transition: box-shadow 0.15s ease; /* Transition for box-shadow */
    box-shadow: 0 2px 5px rgba(0, 0, 0, 0.1); /* Slight shadow by default */
    text-align: center; /* Center content horizontally */
    text-decoration: none; /* Remove underline */
    margin-right: 20px; /* Add margin to create space between boxes */
    margin-bottom: 20px;
  }

  .container:last-child {
    margin-right: 0; /* Remove margin from the last box */
  }

  .container:hover {
    box-shadow: 0 10px 20px rgba(0, 0, 0, 0.1); /* Increased shadow on hover */
  }

  .content {
    width: 100%;
    height: 100%;
    padding: 20px;
    box-sizing: border-box;
  }

  .content img {
    width: 70%;
    height: auto;
    display: block;
    margin: 0 auto; /* Center the image horizontally */
    object-fit: cover; /* Crop the image to cover container */
  }

  .text {
    margin-top: 10px;
    text-align: center; /* Center text within the box */
    text-decoration: none;
  }

  .text h1 {
    font-size: 24px; /* Larger text size */
    margin-top: 1px;
    margin-bottom: 5px; /* Adjust margin between large and small text */
    color: black;
  }
  .text h1:hover {
    color: #2068DC; /* Change text color to blue on hover */
  }

  .text p {
    font-size: 14px;
    margin-top: 5px;
    color: #666;
  }
  <!--  .nba-container { -->
  <!--   background-color: #0E1D2D; -->
  <!-- } -->
</style>
</head>
<body>
  <a href="msu-masters.qmd" class="container">
    <div class="content">
      <img src="img/projects-logos/msu-logo.jpg" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1>MSU Master's - Entomology</h1>
        <p>Co-Advised by David Weaver & Tracy Sterling</p>
      </div>
    </div>
  </a>
  <a href="bballref.qmd" class="container nba-container">
    <div class="content">
      <img src="img/projects-logos/bballref-logo-circle.jpg" alt="Image"> <!-- Center the image within the box -->
      <div class="text">
        <h1><br>NBA Roster Analysis Tool</h1>
        <p></p>
      </div>
    </div>
  </a>
</body>
</html>
```

<!-- ```{=html} -->
<!-- <figure style="display: inline-block; overflow: hidden; position: relative; text-align: center;"> -->
<!--     <a href="bballref.qmd" style="display: block;"> -->
<!--         <img src="img/projects-logos/bballref-logo.jpeg" alt="NBA Roster Analysis Tool" width="200" style="transition: transform 0.3s ease-in-out;"> -->
<!--     </a> -->
<!--     <figcaption style="margin-top: 10px;">NBA Roster Analysis Tool</figcaption> -->
<!-- </figure> -->

<!-- <style> -->
<!--     figure:hover img { -->
<!--         transform: scale(1.05); -->
<!--     } -->
<!-- </style> -->

<!-- ``` -->

### 2024-03-05 running.qmd
Update website 4/5/24

<figure style="margin-right: 20px; display: flex; flex-direction: column; align-items: center;">
  <a href = "tmr50k.qmd">
    <img src="img/tmr50k/tmr50k-top.JPG" alt="Deadhorse Ultra" 
  width = 300" height = "200">
  </a>
  <figcaption style="text-align:center;">Deadhorse Ultra, 2023</figcaption>
</figure>

>>>>

<figure style="margin-right: 20px; display: flex; flex-direction: column; align-items: center;">
  <a href = "tmr50k.qmd">
    <img src="img/tmr50k/tmr50k-top.JPG" alt="Teton Mountain Runs 50K" 
  width = 300" height = "200">
  </a>
  <figcaption style="text-align:center;">Teton Mountain Runs, 2023</figcaption>
</figure>

### 2024-03-05 sb-ww.qmd
Update website 4/5/24

---
title: "Bugs"
output: html_document
---

```{r  echo = F, eval = F}
# Set the directory path
directory_path <- "img/bugs"

# List all the files in the directory
file_names <- list.files(directory_path)

# Exclude files with .zip extension
file_names <- file_names[!grepl("\\.zip$", file_names)]

# Initialize an empty character vector to store the HTML code
html_code <- "<div class=\"gallery\">\n"

# Loop through each file name and generate HTML code
for (i in seq_along(file_names)) {
  # Generate the HTML code for each image
  image_html <- paste0('<img src="', directory_path, "/", file_names[i], '" alt="Image ', i, '" onclick="expandImage(this)">\n')

  # Append the generated HTML code to the existing code
  html_code <- paste(html_code, image_html, sep = "")
}

# Close the gallery div
html_code <- paste(html_code, "</div>\n<div class=\"expanded-container\" onclick=\"closeExpanded()\">\n  <img class=\"expanded\" id=\"expanded-image\" onclick=\"navigateGallery(event)\">\n</div>", sep = "")

# Print the final HTML code
cat(html_code)
```

@@

<div class="gallery">
<img src="img/bugs/blueflowers.JPG" alt="Image 1" onclick="expandImage(this)">
<img src="img/bugs/brownmoth.JPG" alt="Image 2" onclick="expandImage(this)">
<img src="img/bugs/brownred-butterfly.JPG" alt="Image 3" onclick="expandImage(this)">
<img src="img/bugs/butterfly-purpleflower.JPG" alt="Image 4" onclick="expandImage(this)">
<img src="img/bugs/loco-bee.JPG" alt="Image 5" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

@@

</body>
</html>

```

<br>
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Button</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
</style>
</head>
<body>

<!-- Button to download the file -->
<a href="img/bugs/Jackson-Bug-Pics.zip" download="Jackson Bug Pictures">
  <button class="button">Download All Pictures</button>
</a>

</body>
</html>

```

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Image Crop Example</title>
<style>
  .image-container {
    width: 300px; /* Set the width of the container */
    height: 200px; /* Set the height of the container */
    overflow: hidden; /* Hide any overflowing content */
  }
  .cropped-image {
    width: 100%; /* Set the width of the image to fill the container */
    height: auto; /* Automatically adjust the height to maintain aspect ratio */
    object-fit: cover; /* Crop the image to cover the container */
  }
</style>
</head>
<body>

<div class="image-container">
  <img class="cropped-image" src="img/bugs/loco-bee.png" alt="Cropped Image">
</div>

</body>
</html>

```

>>>>

---
title: "smooth brome/winter wheat"
---

@@

<div class="gallery">
<img src="img/msu-masters/cages.HEIC" alt="Image 1" onclick="expandImage(this)">
<img src="img/msu-masters/field.HEIC" alt="Image 2" onclick="expandImage(this)">
<img src="img/msu-masters/vcs.HEIC" alt="Image 3" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

@@

</body>
</html>
```

<div class="gallery">
<img src="img/msu-masters/cages.HEIC" alt="Image 1" onclick="expandImage(this)">
<img src="img/msu-masters/field.HEIC" alt="Image 2" onclick="expandImage(this)">
<img src="img/msu-masters/vcs.HEIC" alt="Image 3" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

</body>
</html>
```

### 2024-03-05 tmr50k.qmd
Update website 4/5/24

::: {style="display: block;"}

```{r get images, echo = F, results = 'asis'}
image_files <- list.files("img/tmr50k", pattern = ".JPG|.png|.gif|.jpg|.jpeg", full.names = TRUE)

for (file in image_files) {
  cat("![](",file, ")\n  \n")
}
```

:::

>>>>

```{r eval = F, echo = F}
# Set the directory path
directory_path <- "img/tmr50k"

# List all the files in the directory
file_names <- list.files(directory_path)

# Exclude files with .zip extension
file_names <- file_names[!grepl("\\.zip$", file_names)]

# Initialize an empty character vector to store the HTML code
html_code <- "<div class=\"gallery\">\n"

# Loop through each file name and generate HTML code
for (i in seq_along(file_names)) {
  # Generate the HTML code for each image
  image_html <- paste0('<img src="', directory_path, "/", file_names[i], '" alt="Image ', i, '" onclick="expandImage(this)">\n')

  # Append the generated HTML code to the existing code
  html_code <- paste(html_code, image_html, sep = "")
}

# Close the gallery div
html_code <- paste(html_code, "</div>\n<div class=\"expanded-container\" onclick=\"closeExpanded()\">\n  <img class=\"expanded\" id=\"expanded-image\" onclick=\"navigateGallery(event)\">\n</div>", sep = "")

# Print the final HTML code
cat(html_code)

```

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Image Gallery</title>
  <style>
    .gallery {
      display: grid;
      grid-template-columns: repeat(auto-fill, minmax(150px, 1fr));
      grid-gap: 10px;
    }
    .gallery img {
      width: 150px;
      height: 150px;
      object-fit: cover; /* Ensure images cover the entire space */
      cursor: pointer;
      transition: transform 0.3s ease;
    }
    .gallery img:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }
    .expanded-container {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.8); /* Semi-transparent background */
      display: none; /* Initially hidden */
      justify-content: center;
      align-items: center;
      z-index: 9999;
    }

    .expanded {
      max-width: 80%;
      max-height: 80%;
      cursor: pointer;
    }
  </style>
</head>
<body>

<div class="gallery">
<img src="img/tmr50k/DSC01450.JPG" alt="Image 1" onclick="expandImage(this)">
<img src="img/tmr50k/DSC01715.JPG" alt="Image 2" onclick="expandImage(this)">
<img src="img/tmr50k/DSC02442.JPG" alt="Image 3" onclick="expandImage(this)">
<img src="img/tmr50k/IMG_0054.JPG" alt="Image 4" onclick="expandImage(this)">
<img src="img/tmr50k/IMG_0088.JPG" alt="Image 5" onclick="expandImage(this)">
<img src="img/tmr50k/IMG_0094.JPG" alt="Image 6" onclick="expandImage(this)">
<img src="img/tmr50k/IMG_0108.JPG" alt="Image 7" onclick="expandImage(this)">
<img src="img/tmr50k/IMG_0120.JPG" alt="Image 8" onclick="expandImage(this)">
<img src="img/tmr50k/IMG_0126.JPG" alt="Image 9" onclick="expandImage(this)">
<img src="img/tmr50k/IMG_5954.JPG" alt="Image 10" onclick="expandImage(this)">
<img src="img/tmr50k/IMG_5983.JPG" alt="Image 11" onclick="expandImage(this)">
<img src="img/tmr50k/IMG_5999.JPG" alt="Image 12" onclick="expandImage(this)">
<img src="img/tmr50k/tmr50k-top.JPG" alt="Image 13" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

<script>
  var currentImageIndex = 0;
  var galleryImages = document.querySelectorAll('.gallery img');

  function expandImage(img) {
    currentImageIndex = Array.from(galleryImages).indexOf(img);
    document.getElementById('expanded-image').src = img.src;
    document.querySelector('.expanded-container').style.display = 'flex';
  }

  function closeExpanded() {
    document.querySelector('.expanded-container').style.display = 'none';
  }

  function navigateGallery(event) {
    // Calculate the click position relative to the expanded image
    var clickX = event.pageX - event.target.getBoundingClientRect().left;
    var imageWidth = event.target.offsetWidth;

    // Determine if the click was on the left or right side of the image
    if (clickX < imageWidth / 2) {
      // Clicked on the left side: navigate to the previous image
      currentImageIndex = (currentImageIndex - 1 + galleryImages.length) % galleryImages.length;
    } else {
      // Clicked on the right side: navigate to the next image
      currentImageIndex = (currentImageIndex + 1) % galleryImages.length;
    }

    // Update the expanded image source
    document.getElementById('expanded-image').src = galleryImages[currentImageIndex].src;
  }

  // Add event listeners to the left and right sides of the expanded image for navigation
  document.querySelector('.expanded').addEventListener('click', function(event) {
    navigateGallery(event);
  });
</script>

</body>
</html>

```
<br>
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Button</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
</style>
</head>
<body>

<!-- Button to download the file -->
<a href="img/tmr50k/tmr2023.zip" download="TetonMountainRuns2023">
  <button class="button">Download All Pictures</button>
</a>

</body>
</html>

```
